Treatment planning for HDR Brachytherapy

### 2015-03-30 Paper Seminar/isim_paper.tex
Conformed usage of "optimization"

\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

@@

\title{Treatment planning for HDR Brachytherapy}
\date{March 31st, 2015}
\author{S.~Elm \and
T.~Karthe \and
M.~E.~Schroeder \and
D.~Golebiewski \and
L.~Mordhorst
}

\maketitle
\newpage

@@

\subsubsection{Optimisation}
\label{subsubsec:optimisation}
The calculation of the fitness-function, as described in equation \eqref{eq:fifu}, is shown in algorithm \ref{alg:fifu}. It is easily seen that it iterates over every voxel in the body. This results in a very high computational complexity and runtime. To improve the performance of the algorithm, three different optimisation approaches are introduced. \\

@@

\paragraph{Scaling and Accuracy}~\\
The fitness-function for the given optimisation problem has very high computational complexity. Hence, two scaling parameters are introduced to achieve shorter runtimes. The challenge here is to find a compromise between good accuracy for the optimisation and practicable runtimes.\\ The first parameter is the treatment range. It chooses the range around the PTV which shall be evaluated by the algorithm. The second parameter is a simple scaling value which defines that just every  n$th$ voxel is evaluated within the treatment range.

>>>>

\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1
]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}

@@

\input{title.tex}

@@

\subsubsection{Optimization}
\label{subsubsec:optimization}
The calculation of the fitness-function, as described in equation \eqref{eq:fifu}, is shown in algorithm \ref{alg:fifu}. It is easily seen that it iterates over every voxel in the body. This results in a very high computational complexity and runtime. To improve the performance of the algorithm, three different optimization approaches are introduced. \\

@@

\paragraph{Scaling and Accuracy}~\\
The fitness-function for the given optimization problem has very high computational complexity. Hence, two scaling parameters are introduced to achieve shorter runtimes. The challenge here is to find a compromise between good accuracy for the optimization and practicable runtimes.\\ The first parameter is the treatment range. It chooses the range around the PTV which shall be evaluated by the algorithm. The second parameter is a simple scaling value which defines that just every  n$th$ voxel is evaluated within the treatment range.
